### 2021-07-01 paper.tex
duality chains modified
Yunqin's corrections

Importantly, $\Spin(2n_c)$ and $\SO(2n_c)_\pm$  gauge theories with $2n_f$ flavors with the same $n_c$ and $n_f$ form a single orbit under this $\SL(2,\bZ)$ action.
More precisely, we need to make the distinction between $\Spin(2n_c)$ and $T(\Spin(2n_c))$ and  similarly between $\SO(2n_c)_\pm$ and $T(\SO(2n_c)_\pm)$, respectively.
Here the theories with $T$ prepended are different from the original ones only by its coupling to the background.
Then we have the following chain of actions: \begin{equation}
{\scriptstyle S} \ \rotatebox[]{-90}{$\circlearrowleft$}\hspace{2mm}
T(\Spin) \stackrel{T}{\longleftrightarrow} 
\Spin \stackrel{S}{\longleftrightarrow} 
\SO_+ \stackrel{T}{\longleftrightarrow} 
T(\SO_+) \stackrel{S}{\longleftrightarrow} 
T(\SO_-) \stackrel{T}{\longleftrightarrow} 
\SO_- \hspace{1mm}\rotatebox[]{90}{$\circlearrowleft$} \ {\scriptstyle S}.
\end{equation}

@@

Let us now determine how the $\SL(2,\bZ_2)$ action affects these data.
The case `none' is very easy.
The additional $\bZ_2$ factor plays no role, and we find the chain of actions given by \begin{equation}
\text{none} \stackrel{T}{\longleftrightarrow} 
\text{none} \stackrel{S}{\longleftrightarrow} 
\text{none} \stackrel{T}{\longleftrightarrow} 
\text{none} \stackrel{S}{\longleftrightarrow} 
\text{none} \stackrel{T}{\longleftrightarrow} 
\text{none} \hspace{1mm}\rotatebox[]{90}{$\circlearrowleft$} \ {\scriptstyle S}
\label{trivial-chain}.
\end{equation}

@@

Combined, the preceding arguments allow us to see the chain of actions \begin{equation}
\text{\Textended} \stackrel{T}{\longleftrightarrow} 
\text{extended} \stackrel{S}{\longleftrightarrow} 
\text{anomaly} \stackrel{T}{\longleftrightarrow} 
\text{anomaly} \stackrel{S}{\longleftrightarrow} 
\text{extended}\stackrel{T}{\longleftrightarrow} 
\text{\Textended}\hspace{1mm}\rotatebox[]{90}{$\circlearrowleft$} \ {\scriptstyle S}.
\label{nontrivial-chain}
\end{equation}

@@

For even $n_c$, the anomaly should be given by  \begin{equation}
\alpha= 2\pi i \cdot \frac12 w_2 \beta a_2
\end{equation}
where $w_2,a_2\in H^2(X;\bZ_2)$ controls the lift from $\SO(2n_c)/\bZ_2$ to $\SO(2n_c)$
and from $\USp(2n_f)/\bZ_2$ to $\USp(2n_f)$, respectively.
For odd $n_c$, the anomaly cochain should be given by 
 \begin{equation}
\alpha'=2\pi i \cdot \frac12 v_2 \beta_2 v_2
\end{equation} where $v_2$ is the class in $H^2(X;\bZ_2)$ which is the mod-2 reduction of
the class $x_2 \in H^2(X;\bZ_4)$ controlling the lift from $\SO(2n_c)/\bZ_2=\Spin(2n_c)/\bZ_4$ to $\Spin(2n_c)$.
We note that $\alpha'$ is exact, but as explained in the previous section, this still affects the gauging process.

>>>>

Importantly, $\Spin(2n_c)$ and $\SO(2n_c)_\pm$  gauge theories with $2n_f$ flavors with the same $n_c$ and $n_f$ form a single orbit under this $\SL(2,\bZ)$ action.
More precisely, we need to make the distinction between $\Spin(2n_c)$ and $T(\Spin(2n_c))$ and  similarly between $\SO(2n_c)_\pm$ and $T(\SO(2n_c)_\pm)$, respectively.
Here the theories with $T$ prepended are different from the original ones only by its coupling to the background.
Then we have the following chain of actions: \begin{equation}
\begin{tikzpicture}
	\node at (0,0) {$
		T(\Spin) \stackrel{T}{\longleftrightarrow} 
		\Spin \stackrel{S}{\longleftrightarrow} 
		\SO_+ \stackrel{T}{\longleftrightarrow} 
		T(\SO_+) \stackrel{S}{\longleftrightarrow} 
		T(\SO_-) \stackrel{T}{\longleftrightarrow} 
		\SO_-.
	$};
	\draw[->] (-5,-1) -- (-5,-0.5);
	\draw[->] (5.4,-1) -- (5.4,-0.5);
	\draw (-5,-1) -- node[above] {\scriptsize $S$} (5.4,-1);
\end{tikzpicture}
\end{equation}

@@

Let us now determine how the $\SL(2,\bZ_2)$ action affects these data.
The case `none' is very easy.
The additional $\bZ_2$ factor plays no role, and we find the chain of actions given by \begin{equation}
\begin{tikzpicture}
	\node at (0,0) {$
		\text{none} \stackrel{T}{\longleftrightarrow} 
		\text{none} \stackrel{S}{\longleftrightarrow} 
		\text{none} \stackrel{T}{\longleftrightarrow} 
		\text{none} \stackrel{S}{\longleftrightarrow} 
		\text{none} \stackrel{T}{\longleftrightarrow} 
		\text{none}.
	$};
	\draw[->] (-4.6,-1) -- (-4.6,-0.5);
	\draw[->] (4.5,-1) -- (4.5,-0.5);
	\draw (-4.6,-1) -- node[above] {\scriptsize $S$} (4.5,-1);
\end{tikzpicture}
\label{trivial-chain}
\end{equation}

@@

Combined, the preceding arguments allow us to see the chain of actions \begin{equation}
\begin{tikzpicture}
	\node at (0,0) {$
		\text{\Textended} \stackrel{T}{\longleftrightarrow} 
		\text{extended} \stackrel{S}{\longleftrightarrow} 
		\text{anomaly} \stackrel{T}{\longleftrightarrow} 
		\text{anomaly} \stackrel{S}{\longleftrightarrow} 
		\text{extended}\stackrel{T}{\longleftrightarrow} 
		\text{\Textended}.
	$};
	\draw[->] (-6.5,-1) -- (-6.5,-0.5);
	\draw[->] (6.3,-1) -- (6.3,-0.5);
	\draw (-6.5,-1) -- node[above] {\scriptsize $S$} (6.3,-1);
\end{tikzpicture}
\label{nontrivial-chain}
\end{equation}

@@

For even $n_c$, the anomaly should be given by  \begin{equation}
\alpha= 2\pi i \cdot \frac12 w_2 \beta a_2
\end{equation}
where $w_2,a_2\in H^2(X;\bZ_2)$ controls the lift from $\SO(2n_c)$ to $\Spin(2n_c)$
and from $\USp(2n_f)/\bZ_2$ to $\USp(2n_f)$, respectively.
For odd $n_c$, the anomaly cochain should be given by 
 \begin{equation}
\alpha'=2\pi i \cdot \frac12 v_2 \beta_2 v_2
\end{equation} where $v_2$ is the class in $H^2(X;\bZ_2)$ which is the mod-2 reduction of
the class $x_2 \in H^2(X;\bZ_4)$ controlling the lift from $\SO(2n_c)/\bZ_2=\Spin(2n_c)/\bZ_4$ to $\Spin(2n_c)$.
We note that $\alpha'$ is exact, but as explained in the previous section, this still affects the gauging process.
